\documentclass{article}
\title{Corporation – Bylaws}
\author{Kwartzlab Society Inc.}
\date{}
\begin{document}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\Alph{subsection}}

\maketitle

\section{Definitions}
\begin{enumerate}
\item ``members meeting'' shall also include annual meetings and general meetings.
\end{enumerate}

\section{Membership}

\subsection{Admittance to Membership}

\begin{enumerate}
\item Persons wishing to become members of KwartzLab must file an application with the Board. The Board shall determine the form of the application. The Board shall notify the membership via the ``Members'' mailing list when they receive such an application.
\item A person who has fulfilled the requirements of paragraph 1 may be admitted to membership by a resolution of Board at a meeting duly called for that purpose. The Board must give notice to the ``Members'' mailing list at least five calendar days before the resolution is to be considered by the Board.
\item A person admitted to membership by the Board of Directors shall have no privileges until their initial dues and first monthly dues are paid. The Board may by resolution set a schedule for pro-rated dues for the first month of membership, based on the date of the member's approval.
\end{enumerate}

\subsection{Dues}

\begin{enumerate}
\item The Board of Directors may by resolution set the dues for the corporation, which may be either or both of:
	\begin{enumerate}
	\item Initial dues, i.e. dues which are payable before a person can become a member;
	\item Monthly dues, i.e. dues which are recurring and payable on the last day of each month (for the following month).
	\end{enumerate}
\item If the Board passes a resolution which raises the initial or monthly dues by more than 10\%, that resolution is effective only until confirmed at a general meeting of the Corporation duly called for that purpose. Such a meeting must be held within 30 days of the initial adoption of the resolution. If the resolution is not confirmed within 30 days, the resolution shall be rendered invalid.
\end{enumerate}

\subsection{Membership Hiatus}

\begin{enumerate}
\item A member may apply to the Board to have their membership placed on hiatus for a period of no less than two months. Such application must specify the start and end dates of the hiatus. The Board may approve a member’s hiatus by resolution at meeting of the Board.
\item During the time a member is on hiatus, they are not required to pay dues, nor shall they have any of the privileges afforded a member, except for the privilege of voting at members meetings called after the hiatus was requested.
\item A member may voluntarily terminate their hiatus at any time by notifying the Board of Directors they wish to do so and paying their monthly dues for the current month. No discounts shall be given for partial months.
\end{enumerate}

\subsection{Suspension or Termination of Memberships}

\begin{enumerate}
\item KwartzLab may suspend or terminate the membership of a member by passing a special resolution (2/3 vote) at a general meeting duly called for that purpose. A suspended member shall have no privileges of membership during the time of the suspension. All dues shall continue to be assessed for suspended members.
\item A resolution under paragraph 1 is not valid unless:
	\begin{enumerate}
	\item Prior written notice is given to the member setting forth the grounds on which the suspension or termination is sought;
	\item This notice is given to the member no fewer than 10 calendar days before the general meeting called to consider the resolution of suspension or termination;
	\item an opportunity is given to the member to appear, either personally or by a person authorized under the Law Society Act to represent the member, to make submissions at the general meeting called to consider the resolution of suspension or termination of that member.
	\end{enumerate}
\item Suspension for Minor Infractions
	\begin{enumerate}
	\item The Board of Directors may suspend a member for a term of no greater than one month by resolution at a meeting of the Board duly called for that purpose if:
		\begin{enumerate}
		\item The member is in arrears on their monthly dues.
		\end{enumerate}
	\item A resolution under sub-paragraph a. is not valid unless:
		\begin{enumerate}
		\item The member is given notice setting forth the grounds on which the suspension is sought (email notice shall be sufficient);
		\item This notice is given to the member no fewer than five calendar days before the meeting of the board of directors called to consider the resolution;
		\item an opportunity is given to the member to appear, either personally or by a person authorized under the Law Society Act to represent the member, to make submissions at the meeting of the board called to consider the resolution.
		\end{enumerate}
	\item If the member suspended under this paragraph rectifies all the condition(s) in sub-paragraph a) for which they were suspended, the Board shall forthwith take any action required to restore that member’s status.
	\end{enumerate}
\end{enumerate}
\subsection{Should a member not pay their dues for at least two consecutive month, then after repeatedly attempting to contact said member by all methods of contact the member has provided for the membership register, including at least once by pre-paid registered mail to the address in the membership register, the Board may by resolution declare the membership abandoned. Abandonded memberships are considered terminated.}

\section{Board of Directors and Officers of the Corporation}

\subsection{Composition and Meetings}

\begin{enumerate}
\item The affairs of KwartzLab shall be managed by a Board of Directors, each of whom must be members of KwartzLab. The Board shall normally consist of seven (7) members, who shall be elected from the membership of KwartzLab at the annual meeting.
\item The Term of Office of the Directors of the Corporation shall begin July 1st, and end June 30th or when their successor has been elected, whichever comes later.
\item Should a vacancy occur on the Board of Directors, the remaining Directors may appoint any eligible member to fill the vacancy for the rest of the term of that Director. Should there not be enough Directors to constitute quorum, the remaining Directors shall be given the power to call a general meeting to elect additional directors.
\item Meetings of the Board of Directors may be called by the President, by any two other Directors, or by resolution at a previous meeting. Notice of meetings must be delivered, telephoned, or emailed to each Director before the meeting is to be held. No formal notice of a meeting is required if all Directors are present or if those absent have given their consent to the meeting being held in their absence.
\item A majority of the normal number of Directors shall constitute quorum at a meeting of the Board of Directors.
\end{enumerate}

\subsection{Election and Removal}

\begin{enumerate}
\item Election of the Directors shall be carried out at the annual meeting.
\item The Board shall solicit nominations for the subsequent Board at least four weeks before the general meeting. Nominations shall remain open for at least two weeks. Members may self-nominate, or be nominated by another member. Nominations shall be signed by the nominee indicating acceptance of the nomination and include the following declarations:
	\begin{enumerate}
	\item That the nominee is eighteen years of age or older;
	\item that the nominee is a permanent resident of Canada; and
	\item that the nominee is not an undischarged bankrupt.
	\end{enumerate}
\item The Board shall announce to the membership at least two weeks before the annual meeting the list of nominees for the Board of Directors.
\item After the close of the nominations period, the Board of Directors shall appoint a election coordinator, who shall be a member of KwartzLab not among the list of nominees to the Board, to oversee the election process. The election coordinator shall be responsible for preparing the physical ballots for the annual meeting.
\item Nominees may withdraw their nomination at any time by contacting the election coordinator.
\item Directors shall be elected at the annual meeting by secret ballot. The election coordinator shall appoint two scrutineers, who must be approved by the meeting, to count the ballots. The election coordinator shall resolve any disputes between the scrutineers.
\item Directors may be removed from office by a special resolution (2/3 vote) passed at a general meeting duly called for that purpose.
\end{enumerate}

\subsection{Officers of the Corporation}

\begin{enumerate}
\item The Board shall choose four officers for the corporation: The President, The Chair of the Board, the Secretary, and the Treasurer. One person may hold more than one office.
\item President
	\begin{enumerate}
	\item The President shall be elected by the Board from the Directors of the Corporation.
	\item The President shall be the Chief Executive Officer of the Corporation.
	\item The President shall ensure that the Corporation follows all of its by-laws and procedures, and if necessary provide interpretation of same.
	\item The President shall be one of three signing authorities of the Corporation.
	\item The President shall provide input to the Chair on Board meeting agendas, and shall approve all agendas drafted by the Chair for members meetings.
	\end{enumerate}
\item Chair of the Board
	\begin{enumerate}
	\item The Chair of the Board shall be elected by the Board from the Directors of the Corporation.
	\item The Chair of the Board shall preside as chair over all meetings of the Board of Directors and members meetings of the Corporation.
	\item The Chair of the Board shall set all agendas for meetings of the Board of Directors; and shall, with the assistance of the President and Secretary, prepare agendas for members meetings of the Corporation, subject to approval by the President.
	\end{enumerate}
\item Secretary
	\begin{enumerate}
	\item The Secretary shall be appointed by the Board from the membership of the Corporation.
	\item The Secretary shall ensure that minutes of all Board meetings and members meetings are kept and brought to the Board for approval.
	\item The Secretary shall maintain the membership register.
	\item The Secretary shall announce all new membership applications to the membership.
	\item The Secretary shall be familiar with the by-laws and procedures of the Corporation and advise the Board on such matters.
	\end{enumerate}
\item Treasurer
	\begin{enumerate}
	\item The Treasurer shall be elected by the Board from the Directors of the Corporation.
	\item The Treasurer shall maintain the financial books of the Corporation.
	\item The Treasurer shall ensure that all bills are paid on time.
	\item The Treasurer shall inform the Board of any members who are in arrears of their dues.
	\item The Treasurer shall present a report on the current finances of the Corporation to the Board on request.
	\item The Treasurer shall prepare a report on the financial status of the Corporation as of the end of each financial year to be presented at the annual meeting which includes:
		\begin{enumerate}
		\item a statement of profit and loss;
		\item a statement of surplus; and
		\item the balance sheet of the corporation.
		\end{enumerate}
	\end{enumerate}
\item The term of office of all officers shall end on June 30th. Despite this, officers shall continue in an interim capacity until the Board of Directors elects or appoints their successor.
\item The Board shall at its earliest opportunity elect or appoint all officers of the corporation where those offices are currently vacant or being filled in an interim capacity.
\item The Board may, by resolution, remove any officer from their office.
\end{enumerate}

\section{Meetings of Members}

\begin{enumerate}
\item KwartzLab may give notice of any members meeting via email to the address on record with the corporation as recorded on the ``Announce'' mailing list, and this shall constitute sufficient notice for the meeting.
	\begin{enumerate}
	\item Notice of any members meeting shall be given at least ten calendar days before the meeting.
	\item Notice for annual and general meetings shall contain the agenda, or a link to the agenda published on the KwartzLab website, for the meeting.
	\end{enumerate}
\item The quorum for members meetings shall be ten members or one quarter of the total membership of KwartzLab Society Inc., whichever is higher.
\item Members may vote by proxy at a general member meeting.  A maximum of three proxy votes may be held at one time by a member in good standing, and the declaration of the proxy vote must be made on the member mailing list in advance of the member meeting.
\item The President;
\item the Treasurer;
\item a third Director to be appointed by the Board.
\end{enumerate}

\section{All expenditures of KwartzLab must be approved by the Board, either directly or by delegation to an officer or committee.}

\section{The financial year of KwartzLab will end on December 31st of each year.}

\end{document}
